### 2022-01-24 doc/contrastive-learning.tex
updates results with new batch sizes
adds entropy semantic segmentation eval results
adds delta results
adds cluster results
updates delta results
update cluster results
updates results

batch size: 16
accumulate gradient: 3
learning rate: 0.2
iterations: 4000

@@

\begin{center}
    \begin{table}[h!]
        \resizebox{\textwidth}{!}{
            \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                              & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU           \\
                \hline
                baseline      & 0.869          & 0.95           & 0.798          & \textbf{0.001} & 0.253          & \textbf{0.585} & 0.510          & 0.731          & \textbf{0.841} & 0.391          & 0.715          & \textbf{0.725} & 0.534          & 0.608          \\
                PointContrast & \textbf{0.895} & \textbf{0.961} & \textbf{0.817} & 0              & \textbf{0.350} & 0.561          & \textbf{0.671} & \textbf{0.737} & 0.834          & \textbf{0.572} & \textbf{0.727} & 0.699          & \textbf{0.554} & \textbf{0.644}
            \end{tabular}
        }
        \caption{S3DIS pretraining results on Semantic Segmentation}
    \end{table}
\end{center}

>>>>

\begin{itemize}
    \item batch size: 6
    \item accumulate gradient: 8
    \item learning rate: 0.2
    \item iterations: 4000
\end{itemize}

@@

\begin{center}
    \begin{table}[h!]
        \resizebox{\textwidth}{!}{
            \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                  & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU           \\
                \hline
                Baseline          & 0.862          & 0.947          & 0.811          & \textbf{0.002} & \textbf{0.356} & 0.551          & 0.590          & 0.745          & 0.751          & 0.452          & 0.719          & 0.606          & 0.514          & 0.608          \\
                PointContrast     & \textbf{0.905} & \textbf{0.962} & \textbf{0.818} & 0              & 0.345          & \textbf{0.581} & \textbf{0.633} & \textbf{0.750} & \textbf{0.861} & \textbf{0.648} & \textbf{0.729} & \textbf{0.799} & \textbf{0.566} & \textbf{0.661} \\
                \hline
                Entropy           & \textbf{0.912} & 0.961          & \textbf{0.828} & 0              & 0.307          & 0.513          & 0.626          & 0.746          & 0.853          & 0.634          & \textbf{0.742} & 0.761          & \textbf{0.576} & 0.651          \\
                Delta             & \textbf{0.924} & 0.959          & 0.817          & 0              & \textbf{0.388} & \textbf{0.611} & 0.563          & \textbf{0.770} & \textbf{0.867} & \textbf{0.667} & \textbf{0.742} & 0.635          & \textbf{0.587} & 0.656          \\
                Custer            & \textbf{0.924} & 0.957          & 0.814          & 0              & \textbf{0.373} & 0.562          & \textbf{0.688} & \textbf{0.776} & 0.844          & 0.524          & 0.729          & 0.717          & 0.587          & 0.653          \\
                \hline
                Debiased          & 0.910          & 0.958          & 0.811          & \textbf{0.001} & 0.260          & 0.537          & 0.655          & 0.745          & 0.859          & 0.555          & 0.699          & 0.770          & 0.562          & 0.640          \\
                Debiased++        & 0.901          & 0.961          & 0.815          & \textbf{0.008} & 0.286          & 0.586          & 0.683          & 0.745          & 0.855          & 0.599          & 0.716          & 0.779          & 0.554          & 0.653          \\
                \hline
                Sampling - Hard   & 0.904          & 0.959          & 0.824          & 0              & 0.361          & 0.579          & 0.659          & 0.731          & 0.837          & 0.505          & 0.697          & 0.711          & 0.557          & 0.640          \\
                Sampling - Easy   & 0.666          & 0.952          & 0.779          & 0              & 0.201          & 0              & 0              & 0.740          & 0              & 0              & 0.690          & 0.784          & 0.526          & 0.411          \\
                Sampling - Mixing & 0.895          & 0.962          & \textbf{0.820} & 0              & 0.277          & 0.576          & \textbf{0.706} & 0.747          & 0.849          & 0.567          & 0.724          & 0.769          & 0.562          & 0.650          \\
            \end{tabular}
        }
        \caption{S3DIS pretraining results on Semantic Segmentation}
    \end{table}
\end{center}
